What the hell is the title of this paper?

### 2018-05-14 NIPS 2018/main.tex

\begin{figure*}[t] 
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=3cm, width=2.0cm]{images/rooms2.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) the rooms environment, (b) transfer from $10$ source tasks with both doors moving, (c) transfer from $10$ source tasks with only one door moving, and (d) transfer performance as a function of how likely the target task is according to the prior.}
  \label{fig:dipfdbsgraphplots}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=3cm, width=2.0cm]{images/maze/maze6.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) Sample Maze (Maze 6), (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 6 and 13---see App. \ref{}.}
  \label{fig:ccmazeplots}
\end{figure*}

>>>>

\begin{figure*}[t] 
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) the rooms environment, (b) transfer from $10$ source tasks with both doors moving, (c) transfer from $10$ source tasks with only one door moving, and (d) transfer performance as a function of how likely the target task is according to the prior.}
  \label{fig:dipfdbsgraphplots}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{subfigure}[b]{0.15\textwidth}
    \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm,clip=true,height=2.6cm, width=2.0cm]{images/maze/maze6.png}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev.pdf}
    \caption{}
  \end{subfigure}
  \caption{(a) Sample Maze (Maze 6), (b) transfer from $10$ sources in Cartpole, (c) transfer from $10$ source tasks in Mountain Car, and (d) transfer from $10$ sources in Mazes 6 and 13---see App. \ref{}.}
  \label{fig:ccmazeplots}
\end{figure*}
